## CAT-2B-2B-INT

### Overall model fit

```{r, fig.height=58.5, fig.width=10}
power_overall_plot_between_cat(between_cat_list[['CAT-2B-2B-INT']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_between_cat(between_cat_list[['CAT-2B-2B-INT']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_between_cat(between_cat_list[['CAT-2B-2B-INT']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_between_cat(between_cat_list[['CAT-2B-2B-INT']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B-2B-INT']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B-2B-INT']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=58.5, fig.width=10}
ci_width_plot_between_cat(between_cat_list[['CAT-2B-2B-INT']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_between_cat(between_cat_list[['CAT-2B-2B-INT']]$sim_df_model_errors_sum)
```




## CAT-2B-2B

### Overall model fit

```{r, fig.height=58.5, fig.width=10}
power_overall_plot_between_cat(between_cat_list[['CAT-2B-2B']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_between_cat(between_cat_list[['CAT-2B-2B']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_between_cat(between_cat_list[['CAT-2B-2B']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_between_cat(between_cat_list[['CAT-2B-2B']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B-2B']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B-2B']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=58.5, fig.width=10}
ci_width_plot_between_cat(between_cat_list[['CAT-2B-2B']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_between_cat(between_cat_list[['CAT-2B-2B']]$sim_df_model_errors_sum)
```




## CAT-2B-3B-INT

### Overall model fit

```{r, fig.height=58.5, fig.width=10}
power_overall_plot_between_cat(between_cat_list[['CAT-2B-3B-INT']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_between_cat(between_cat_list[['CAT-2B-3B-INT']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_between_cat(between_cat_list[['CAT-2B-3B-INT']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_between_cat(between_cat_list[['CAT-2B-3B-INT']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B-3B-INT']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B-3B-INT']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=58.5, fig.width=10}
ci_width_plot_between_cat(between_cat_list[['CAT-2B-3B-INT']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_between_cat(between_cat_list[['CAT-2B-3B-INT']]$sim_df_model_errors_sum)
```




## CAT-2B-3B

### Overall model fit

```{r, fig.height=58.5, fig.width=10}
power_overall_plot_between_cat(between_cat_list[['CAT-2B-3B']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_between_cat(between_cat_list[['CAT-2B-3B']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_between_cat(between_cat_list[['CAT-2B-3B']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_between_cat(between_cat_list[['CAT-2B-3B']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B-3B']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B-3B']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=58.5, fig.width=10}
ci_width_plot_between_cat(between_cat_list[['CAT-2B-3B']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_between_cat(between_cat_list[['CAT-2B-3B']]$sim_df_model_errors_sum)
```




## CAT-2B

### Overall model fit

```{r, fig.height=35.1, fig.width=10}
power_overall_plot_between_cat(between_cat_list[['CAT-2B']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=35.1, fig.width=10}
power_plot_between_cat(between_cat_list[['CAT-2B']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=35.1, fig.width=10}
bias_mean_plot_between_cat(between_cat_list[['CAT-2B']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=35.1, fig.width=10}
bias_sd_plot_between_cat(between_cat_list[['CAT-2B']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=35.1, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=35.1, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-2B']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=35.1, fig.width=10}
ci_width_plot_between_cat(between_cat_list[['CAT-2B']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=35.1, fig.width=10}
model_errors_plot_between_cat(between_cat_list[['CAT-2B']]$sim_df_model_errors_sum)
```




## CAT-3B-3B-INT

### Overall model fit

```{r, fig.height=58.5, fig.width=10}
power_overall_plot_between_cat(between_cat_list[['CAT-3B-3B-INT']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_between_cat(between_cat_list[['CAT-3B-3B-INT']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_between_cat(between_cat_list[['CAT-3B-3B-INT']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_between_cat(between_cat_list[['CAT-3B-3B-INT']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-3B-3B-INT']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-3B-3B-INT']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=58.5, fig.width=10}
ci_width_plot_between_cat(between_cat_list[['CAT-3B-3B-INT']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_between_cat(between_cat_list[['CAT-3B-3B-INT']]$sim_df_model_errors_sum)
```




## CAT-3B-3B

### Overall model fit

```{r, fig.height=58.5, fig.width=10}
power_overall_plot_between_cat(between_cat_list[['CAT-3B-3B']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_between_cat(between_cat_list[['CAT-3B-3B']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_between_cat(between_cat_list[['CAT-3B-3B']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_between_cat(between_cat_list[['CAT-3B-3B']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-3B-3B']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=58.5, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-3B-3B']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=58.5, fig.width=10}
ci_width_plot_between_cat(between_cat_list[['CAT-3B-3B']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_between_cat(between_cat_list[['CAT-3B-3B']]$sim_df_model_errors_sum)
```




## CAT-3B

### Overall model fit

```{r, fig.height=35.1, fig.width=10}
power_overall_plot_between_cat(between_cat_list[['CAT-3B']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=35.1, fig.width=10}
power_plot_between_cat(between_cat_list[['CAT-3B']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=35.1, fig.width=10}
bias_mean_plot_between_cat(between_cat_list[['CAT-3B']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=35.1, fig.width=10}
bias_sd_plot_between_cat(between_cat_list[['CAT-3B']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=35.1, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-3B']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=35.1, fig.width=10}
cover_plot_between_cat(between_cat_list[['CAT-3B']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=35.1, fig.width=10}
ci_width_plot_between_cat(between_cat_list[['CAT-3B']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=35.1, fig.width=10}
model_errors_plot_between_cat(between_cat_list[['CAT-3B']]$sim_df_model_errors_sum)
```




