## N-NUM-CAT-INT (1 continuous predictors)

### Overall model fit

```{r, fig.height=764.4, fig.width=10}
power_overall_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_overall_sum |> dplyr::filter(n_cont_preds ==1))
```



### Power/false-positives

```{r, fig.height=764.4, fig.width=10}
power_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_power_sum |> dplyr::filter(n_cont_preds ==1))
```



### Bias 

#### Mean bias 

```{r, fig.height=764.4, fig.width=10}
bias_mean_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==1))
```



#### SD bias 

```{r, fig.height=764.4, fig.width=10}
bias_sd_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==1))
```



### CI coverage

```{r, fig.height=764.4, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_cover_sum |> dplyr::filter(n_cont_preds ==1))
```



### CI bias-shifted coverage

```{r, fig.height=764.4, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_cover_shift_sum |> dplyr::filter(n_cont_preds ==1))
```



### CI width

```{r, fig.height=764.4, fig.width=10}
ci_width_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_ci_width_sum |> dplyr::filter(n_cont_preds ==1))
```



### Model errors

```{r, fig.height=764.4, fig.width=10}
model_errors_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_model_errors_sum |> dplyr::filter(n_cont_preds ==1))
```




## N-NUM-CAT-INT (3 continuous predictors)

### Overall model fit

```{r, fig.height=764.4, fig.width=10}
power_overall_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_overall_sum |> dplyr::filter(n_cont_preds ==3))
```



### Power/false-positives

```{r, fig.height=764.4, fig.width=10}
power_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_power_sum |> dplyr::filter(n_cont_preds ==3))
```



### Bias 

#### Mean bias 

```{r, fig.height=764.4, fig.width=10}
bias_mean_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==3))
```



#### SD bias 

```{r, fig.height=764.4, fig.width=10}
bias_sd_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==3))
```



### CI coverage

```{r, fig.height=764.4, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_cover_sum |> dplyr::filter(n_cont_preds ==3))
```



### CI bias-shifted coverage

```{r, fig.height=764.4, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_cover_shift_sum |> dplyr::filter(n_cont_preds ==3))
```



### CI width

```{r, fig.height=764.4, fig.width=10}
ci_width_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_ci_width_sum |> dplyr::filter(n_cont_preds ==3))
```



### Model errors

```{r, fig.height=764.4, fig.width=10}
model_errors_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_model_errors_sum |> dplyr::filter(n_cont_preds ==3))
```




## N-NUM-CAT-INT (8 continuous predictors)

### Overall model fit

```{r, fig.height=764.4, fig.width=10}
power_overall_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_overall_sum |> dplyr::filter(n_cont_preds ==8))
```



### Power/false-positives

```{r, fig.height=764.4, fig.width=10}
power_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_power_sum |> dplyr::filter(n_cont_preds ==8))
```



### Bias 

#### Mean bias 

```{r, fig.height=764.4, fig.width=10}
bias_mean_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==8))
```



#### SD bias 

```{r, fig.height=764.4, fig.width=10}
bias_sd_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==8))
```



### CI coverage

```{r, fig.height=764.4, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_cover_sum |> dplyr::filter(n_cont_preds ==8))
```



### CI bias-shifted coverage

```{r, fig.height=764.4, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_cover_shift_sum |> dplyr::filter(n_cont_preds ==8))
```



### CI width

```{r, fig.height=764.4, fig.width=10}
ci_width_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_ci_width_sum |> dplyr::filter(n_cont_preds ==8))
```



### Model errors

```{r, fig.height=764.4, fig.width=10}
model_errors_plot_between_cat(between_mixed_list[['N-NUM-CAT-INT']]$sim_df_model_errors_sum |> dplyr::filter(n_cont_preds ==8))
```




## N-NUM-CAT (1 continuous predictors)

### Overall model fit

```{r, fig.height=772.2, fig.width=10}
power_overall_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_overall_sum |> dplyr::filter(n_cont_preds ==1))
```



### Power/false-positives

```{r, fig.height=772.2, fig.width=10}
power_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_power_sum |> dplyr::filter(n_cont_preds ==1))
```



### Bias 

#### Mean bias 

```{r, fig.height=772.2, fig.width=10}
bias_mean_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==1))
```



#### SD bias 

```{r, fig.height=772.2, fig.width=10}
bias_sd_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==1))
```



### CI coverage

```{r, fig.height=772.2, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_cover_sum |> dplyr::filter(n_cont_preds ==1))
```



### CI bias-shifted coverage

```{r, fig.height=772.2, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_cover_shift_sum |> dplyr::filter(n_cont_preds ==1))
```



### CI width

```{r, fig.height=772.2, fig.width=10}
ci_width_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_ci_width_sum |> dplyr::filter(n_cont_preds ==1))
```



### Model errors

```{r, fig.height=772.2, fig.width=10}
model_errors_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_model_errors_sum |> dplyr::filter(n_cont_preds ==1))
```




## N-NUM-CAT (3 continuous predictors)

### Overall model fit

```{r, fig.height=772.2, fig.width=10}
power_overall_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_overall_sum |> dplyr::filter(n_cont_preds ==3))
```



### Power/false-positives

```{r, fig.height=772.2, fig.width=10}
power_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_power_sum |> dplyr::filter(n_cont_preds ==3))
```



### Bias 

#### Mean bias 

```{r, fig.height=772.2, fig.width=10}
bias_mean_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==3))
```



#### SD bias 

```{r, fig.height=772.2, fig.width=10}
bias_sd_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==3))
```



### CI coverage

```{r, fig.height=772.2, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_cover_sum |> dplyr::filter(n_cont_preds ==3))
```



### CI bias-shifted coverage

```{r, fig.height=772.2, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_cover_shift_sum |> dplyr::filter(n_cont_preds ==3))
```



### CI width

```{r, fig.height=772.2, fig.width=10}
ci_width_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_ci_width_sum |> dplyr::filter(n_cont_preds ==3))
```



### Model errors

```{r, fig.height=772.2, fig.width=10}
model_errors_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_model_errors_sum |> dplyr::filter(n_cont_preds ==3))
```




## N-NUM-CAT (8 continuous predictors)

### Overall model fit

```{r, fig.height=772.2, fig.width=10}
power_overall_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_overall_sum |> dplyr::filter(n_cont_preds ==8))
```



### Power/false-positives

```{r, fig.height=772.2, fig.width=10}
power_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_power_sum |> dplyr::filter(n_cont_preds ==8))
```



### Bias 

#### Mean bias 

```{r, fig.height=772.2, fig.width=10}
bias_mean_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==8))
```



#### SD bias 

```{r, fig.height=772.2, fig.width=10}
bias_sd_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_bias_sum |> dplyr::filter(n_cont_preds ==8))
```



### CI coverage

```{r, fig.height=772.2, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_cover_sum |> dplyr::filter(n_cont_preds ==8))
```



### CI bias-shifted coverage

```{r, fig.height=772.2, fig.width=10}
cover_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_cover_shift_sum |> dplyr::filter(n_cont_preds ==8))
```



### CI width

```{r, fig.height=772.2, fig.width=10}
ci_width_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_ci_width_sum |> dplyr::filter(n_cont_preds ==8))
```



### Model errors

```{r, fig.height=772.2, fig.width=10}
model_errors_plot_between_cat(between_mixed_list[['N-NUM-CAT']]$sim_df_model_errors_sum |> dplyr::filter(n_cont_preds ==8))
```




