## CAT-2W

### Power/false-positives

```{r, fig.height=11.7, fig.width=10}
power_plot_within_cat(within_cat_list[['CAT-2W']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=11.7, fig.width=10}
bias_mean_plot_within_cat(within_cat_list[['CAT-2W']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=11.7, fig.width=10}
bias_sd_plot_within_cat(within_cat_list[['CAT-2W']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=11.7, fig.width=10}
cover_plot_within_cat(within_cat_list[['CAT-2W']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=11.7, fig.width=10}
cover_plot_within_cat(within_cat_list[['CAT-2W']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=11.7, fig.width=10}
ci_width_plot_within_cat(within_cat_list[['CAT-2W']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=11.7, fig.width=10}
model_errors_plot_within_cat(within_cat_list[['CAT-2W']]$sim_df_model_errors_sum)
```




## CAT-3W

### Overall model fit

```{r, fig.height=11.7, fig.width=10}
power_overall_plot_within_cat(within_cat_list[['CAT-3W']]$sim_df_overall_sum)
```



### Power/false-positives

```{r, fig.height=11.7, fig.width=10}
power_plot_within_cat(within_cat_list[['CAT-3W']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=11.7, fig.width=10}
bias_mean_plot_within_cat(within_cat_list[['CAT-3W']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=11.7, fig.width=10}
bias_sd_plot_within_cat(within_cat_list[['CAT-3W']]$sim_df_bias_sum)
```



### CI coverage

```{r, fig.height=11.7, fig.width=10}
cover_plot_within_cat(within_cat_list[['CAT-3W']]$sim_df_cover_sum)
```



### CI bias-shifted coverage

```{r, fig.height=11.7, fig.width=10}
cover_plot_within_cat(within_cat_list[['CAT-3W']]$sim_df_cover_shift_sum)
```



### CI width

```{r, fig.height=11.7, fig.width=10}
ci_width_plot_within_cat(within_cat_list[['CAT-3W']]$sim_df_ci_width_sum)
```



### Model errors

```{r, fig.height=11.7, fig.width=10}
model_errors_plot_within_cat(within_cat_list[['CAT-3W']]$sim_df_model_errors_sum)
```




## CAT-2W-2B-2B

### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_within_cat(within_cat_list[['CAT-2W-2B-2B']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_within_cat(within_cat_list[['CAT-2W-2B-2B']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_within_cat(within_cat_list[['CAT-2W-2B-2B']]$sim_df_bias_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_within_cat(within_cat_list[['CAT-2W-2B-2B']]$sim_df_model_errors_sum)
```




## CAT-2W-2B

### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_within_cat(within_cat_list[['CAT-2W-2B']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_within_cat(within_cat_list[['CAT-2W-2B']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_within_cat(within_cat_list[['CAT-2W-2B']]$sim_df_bias_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_within_cat(within_cat_list[['CAT-2W-2B']]$sim_df_model_errors_sum)
```




## CAT-2W-2W-2B

### Power/false-positives

```{r, fig.height=58.5, fig.width=10}
power_plot_within_cat(within_cat_list[['CAT-2W-2W-2B']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=58.5, fig.width=10}
bias_mean_plot_within_cat(within_cat_list[['CAT-2W-2W-2B']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=58.5, fig.width=10}
bias_sd_plot_within_cat(within_cat_list[['CAT-2W-2W-2B']]$sim_df_bias_sum)
```



### Model errors

```{r, fig.height=58.5, fig.width=10}
model_errors_plot_within_cat(within_cat_list[['CAT-2W-2W-2B']]$sim_df_model_errors_sum)
```




## CAT-2W-2W-2W

### Power/false-positives

```{r, fig.height=19.5, fig.width=10}
power_plot_within_cat(within_cat_list[['CAT-2W-2W-2W']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=19.5, fig.width=10}
bias_mean_plot_within_cat(within_cat_list[['CAT-2W-2W-2W']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=19.5, fig.width=10}
bias_sd_plot_within_cat(within_cat_list[['CAT-2W-2W-2W']]$sim_df_bias_sum)
```



### Model errors

```{r, fig.height=19.5, fig.width=10}
model_errors_plot_within_cat(within_cat_list[['CAT-2W-2W-2W']]$sim_df_model_errors_sum)
```




## CAT-2W-2W

### Power/false-positives

```{r, fig.height=19.5, fig.width=10}
power_plot_within_cat(within_cat_list[['CAT-2W-2W']]$sim_df_power_sum)
```



### Bias 

#### Mean bias 

```{r, fig.height=19.5, fig.width=10}
bias_mean_plot_within_cat(within_cat_list[['CAT-2W-2W']]$sim_df_bias_sum)
```



#### SD bias 

```{r, fig.height=19.5, fig.width=10}
bias_sd_plot_within_cat(within_cat_list[['CAT-2W-2W']]$sim_df_bias_sum)
```



### Model errors

```{r, fig.height=19.5, fig.width=10}
model_errors_plot_within_cat(within_cat_list[['CAT-2W-2W']]$sim_df_model_errors_sum)
```




